---
title: "Data Example Plots for The Causal Effects of Modified Treatment Policies Under Network Interference"
format: html
---

This Quarto notebook produces publication-ready plots for the *data example* section of Balkus, Delaney, and Hejazi (2025) "The Causal Effects of Modified Treatment Policies Under Network Interference". See `data-mtp.qmd` for the actual analysis of the data. Each sub-section header corresponds to a different plot.

First, we load the data and necessary packages.

```{r}
library(here)
library(tidyverse)
library(mgcv)
library(stargazer)
library(sf)
library(colorspace)
library("scales")

df_raw = read_csv(here("data", "NO2_ZEV_ZCTAs.csv"))
commuters = read_csv(here("data", "ZEV_commuters_2019.csv"))
neighbors = commuters %>% group_by(h_zcta) %>% summarize(`Network degree` = n()) 

df = df_raw %>% left_join(neighbors, by = c("ZCTA" = "h_zcta")) %>% select(-ZCTA, -n2_2019, -p__2013)

```

## Table 1: Summary Statistics

```{r}
tbl = stargazer(as.data.frame(df), summary.stat = c("mean", "median", "p25", "p75"), nobs = F,
                covariate.labels=c("Change in NO2, 2013-2019 (ppb)",
                                   "\\% ZEV (of registered vehicles) , 2019",
                                   "\\% ZEV (of registered vehicles), 2013",
                                   "Population",
                                   "Median age (years)",
                                   "\\% pop. college educated",
                                   "\\% pop. high school educated",
                                   "\\% pop. white",
                                   "Median income (\\$)",
                                   "\\% pop. in poverty",
                                   "\\% of homes owner-occupied",
                                   "Median home value (\\$)",
                                   "\\% pop. who take automobile to work",
                                   "\\% pop. who take public transit to work",
                                   "\\% pop. who work from home",
                                   "Industrial employment (jobs/acre)",
                                   "Road density (per acre)",
                                   "Public transit frequency (peak, per hour)",
                                   "Walkability index"
                ), digits = 1)
```

## Figure 1: Map of Treatment and Outcome

```{r}
# Read in shape data
df_shp = st_read(here("data", "NO2_ZEV_ZCTAs.shp"))
```

### NO2

```{r}
p = ggplot(df_shp) + geom_sf(aes(geometry=geometry, fill = no2), color = NA) + 
  theme(axis.line=element_blank(), 
        axis.text.x=element_blank(), axis.title.x=element_blank(),
        axis.text.y=element_blank(), axis.title.y=element_blank(),
        axis.ticks=element_blank(), 
        panel.background = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank()) + 
  scale_fill_gradientn(
      name = "Change in NO₂, \n2013-2019 (ppb)",
      colors=c("darkblue","#f5f5f5","darkred"),
      values=rescale(c(-3.1,0,1.1)),
      limits=c(-3.1,1.1), oob = scales::squish
    )
ggsave(here("results", "CA-NO2.svg"), plot = p, width = 5, height = 5, units = "in", dpi = 400)
p

```

### ZEV

```{r}

p = ggplot(df_shp) + geom_sf(aes(geometry=geometry, fill = ZEV_2019), color = NA) + 
  theme(axis.line=element_blank(), 
        axis.text.x=element_blank(), axis.title.x=element_blank(),
        axis.text.y=element_blank(), axis.title.y=element_blank(),
        axis.ticks=element_blank(), 
        panel.background = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank()) + 
  scale_fill_gradientn(
    name = "% of ZEV, 2019",
    colors=c("#f5f5f5","limegreen", "darkgreen"),
    values=rescale(c(0,5,21)),
    limits=c(0,21), oob = scales::squish, 
  )

ggsave(here("results", "CA-ZEV.svg"), plot = p, width = 5, height = 5, units = "in", dpi = 400)
p
```

## Figure 2: Full Confounder Comparison

```{r}
theme_set(theme_minimal())

labels = c("Induced MTP (Sum)", "MTP (No Interference)",  "GLM (No Interference)")
estimate_df_a = read_csv(here("results", "mtp_analysis_a.csv"))
estimate_df_a$shifttype = "Additive Shift: 1 unit"
estimate_df_m = read_csv(here("results", "mtp_analysis_m.csv"))
estimate_df_m$shifttype = "Multiplicative Shift: 20%"

estimate_df = rbind(estimate_df_a, estimate_df_m)

estimate_df$method = factor(estimate_df$method, labels)
group.colors <- c("GLM (No Interference)" = "#7BA573", "MTP (No Interference)" = "#7BA573", 
                  "Induced MTP (Sum)" = "#000332")


p = ggplot(estimate_df) + 
  geom_vline(xintercept = 0, color = "darkgray") +
  geom_errorbarh(aes(y = method, xmin = lower, xmax = upper, color = method), 
                 height = .4, linewidth = 0.8) + 
  geom_point(aes(x = effects, y = method, color = method), size = 2.5) +
  facet_wrap(vars(shifttype), ncol = 2, scales = "fixed") + 
  theme(axis.text.x = element_text(margin = margin(t = 4, r = 10, b = 10, l = 10)),
        legend.position = "none", 
        plot.margin = margin(, 4, , , "cm"),
        panel.spacing = unit(2, "lines"),
        strip.text.x = element_text(size = 11),
        panel.grid.major = element_line(size = 0.1),
        panel.grid.minor = element_line(size = 0.1)
) +
  ylab("") + xlab("Mean NO₂ reduction, 2013-2019 (ppb)") +
  scale_color_manual(values=group.colors)
p
ggsave(here("results", "data-MTP-comparison.png"), p, width = 7.5, height = 2.5, dpi = 1000)

```

## Figure 3: MTP Grid

```{r}
grid_df_a = read_csv(here("results", "mtp_grid_a.csv"))
grid_df_a$shifttype = "Additive Shift"

grid_df_m = read_csv(here("results", "mtp_grid_m.csv"))
grid_df_m$shifttype = "Multiplicative Shift"

# First, compute the ratio needed to Bonferroni-correct the existing CIs
original_tstat = 1.96

## additive
num_tests_a = length(unique(grid_df_a$shift))
new_tstat_a = qnorm(1 - (0.025 / num_tests_a))
new_tstat_a
ratio_a = new_tstat_a / original_tstat

grid_df_a$lower = grid_df_a$est - ((grid_df_a$est - grid_df_a$lower) * ratio_a)
grid_df_a$upper = grid_df_a$est + ((grid_df_a$upper - grid_df_a$est) * ratio_a)

## multiplicative
num_tests_m = length(unique(grid_df_m$shift))
new_tstat_m = qnorm(1 - (0.025 / num_tests_m))
ratio_m = new_tstat_m / original_tstat

grid_df_m$lower = grid_df_m$est - ((grid_df_m$est - grid_df_m$lower) * ratio_a)
grid_df_m$upper = grid_df_m$est + ((grid_df_m$upper - grid_df_m$est) * ratio_a)

grid_df = rbind(grid_df_a, grid_df_m)
grid_df = grid_df[grid_df$shift > 0,]

group.colors <- c("MTP (No Interference)" = "#7BA573", 
                  "Induced MTP (Sum)" = "#000332")
                  
```

```{r}
labels = unique(grid_df$name)[c(2, 1, 3)]
grid_df$name  = factor(grid_df$name, levels = labels)


p = ggplot(grid_df, aes(x = shift, y = est)) + 
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = name), 
                 linewidth = 0.6, alpha = 0.3) + 
  geom_line(aes(color = name), linewidth = 0.6) +
  labs(x = "Increase in Proportion of ZEVs Across CA (Percentage Point)", 
       y = "Mean NO₂ reduction, \n2013-2019 (ppb)",
       color="Estimator") + 
  theme(legend.position = "bottom", axis.text.x = element_text(margin = margin(t = 2, r = 8, b = 8, l = 8)), plot.margin = margin(, 1, , , "cm"), strip.text.x = element_text(size = 13),
  panel.grid.major = element_line(size = 0.1),
  panel.grid.minor = element_line(size = 0.1)) + 
  facet_wrap(vars(shifttype), ncol = 2, scales = "free") + 
  scale_color_manual(name = "", labels = labels, values=group.colors) + 
  scale_fill_manual(name = "", labels = labels, values=group.colors)

ggsave(here("results", "data-MTP-grid2.png"), width = 6, height = 3, dpi = 1000)
```
